Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-01 paper/ms.tex
bugfix plot_scene
I'm pretty sure the invert_axis calls on WCSaxes have bugs. Possible
future astropy PR / issue...

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ over Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$ (brighter stars are larger).
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10, with a logarithmic
    grayscale. The yellow star is the position of \tn.  White circles
    are resolved Gaia sources with $T<16$. Brighter stars are larger.
    The black \texttt{X} and white \texttt{/} hatches show the
    apertures used to measure the background and target star flux,
    respectively. Dashed lines of constant declination and right
    ascension are shown.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible
    sources of the transits.
		\label{fig:scene}
	}
\end{figure}
